Comparison among doublet predictions on benchmarking datasets

### 2024-06-03 analyses/doublet-detection/exploratory-notebooks/03_compare-benchmark-results.Rmd
analysis portion of notebook largely completed, and next it needs interpretation

```{r read_data}
confusion_colors <- c(
  "tp" = "lightblue",
  "tn" = "pink",
  "fp" = "blue",
  "fn" = "firebrick2"
)

@@

>>>>

```{r read_data}
# used in PCA plots
confusion_colors <- c(
  "tp" = "lightblue",
  "tn" = "pink",
  "fp" = "blue",
  "fn" = "firebrick2"
)

@@

### Upset plots

This section shows upset plots for overlap among methods for each dataset.

```{r}
pull_barcodes <- function(df, pred_var) {
  # Helper function to pull out barcodes for doublet calls
  df$barcodes[df[[pred_var]] == "doublet"]
}

upset_list <- doublet_df_list |>
  purrr::iwalk(
    \(df, dataset) {

      doublet_barcodes <- list(
        "scDblFinder" = pull_barcodes(df, "scdbl_prediction"),
        "scrublet"    = pull_barcodes(df, "scrublet_prediction"),
        "cxds"        = pull_barcodes(df, "cxds_prediction")
      )

      UpSetR::upset(fromList(doublet_barcodes), order.by = "freq") |> print()
      grid::grid.text( # plot title
        dataset,
        x = 0.65, 
        y = 0.95, 
        gp = grid::gpar(fontsize=16)
      )

    }
  )

```
